\begin{thebibliography}{99}

\bibitem{luo2025hilserl}
Jianlan Luo, Charles Xu, Jeffrey Wu, and Sergey Levine.
\newblock Precise and dexterous robotic manipulation via human-in-the-loop reinforcement learning.
\newblock \emph{arXiv preprint arXiv:2410.21845}, 2024.

\bibitem{ball2023rlpd}
Philip J. Ball, Laura Smith, Ilya Kostrikov, and Sergey Levine.
\newblock Efficient online reinforcement learning with offline data.
\newblock In \emph{Proceedings of the 40th International Conference on Machine Learning}, PMLR 202:1577--1594, 2023.

\bibitem{retzlaff2024hitl}
Carl Orge Retzlaff, Srijita Das, Christabel Wayllace, Payam Mousavi, Mohammad Afshari, Tianpei Yang, Anna Saranti, Alessa Angerschmid, Matthew E. Taylor, and Andreas Holzinger.
\newblock Human-in-the-loop reinforcement learning: A survey and position on requirements, challenges, and opportunities.
\newblock \emph{Journal of Artificial Intelligence Research}, 79:359--415, 2024.

\bibitem{robosuite2020}
Yuke Zhu, Josiah Wong, Ajay Mandlekar, Roberto Martin-Martin, Abhishek Joshi, Kevin Lin, Abhiram Maddukuri, Soroush Nasiriany, and Yifeng Zhu.
\newblock robosuite: A modular simulation framework and benchmark for robot learning.
\newblock \emph{arXiv preprint arXiv:2009.12293}, 2020.

\bibitem{haarnoja2018sac}
Tuomas Haarnoja, Aurick Zhou, Pieter Abbeel, and Sergey Levine.
\newblock Soft Actor-Critic: Off-policy maximum entropy deep reinforcement learning with a stochastic actor.
\newblock In \emph{Proceedings of the 35th International Conference on Machine Learning}, PMLR 80:1861--1870, 2018.

\bibitem{sac2018applications}
Tuomas Haarnoja, Aurick Zhou, Kristian Hartikainen, George Tucker, Sehoon Ha, Jie Tan, Vikash Kumar, Henry Zhu, Abhishek Gupta, Pieter Abbeel, and Sergey Levine.
\newblock Soft Actor-Critic algorithms and applications.
\newblock \emph{arXiv preprint arXiv:1812.05905}, 2018.

\bibitem{mandlekar2021robomimic}
Ajay Mandlekar, Danfei Xu, Josiah Wong, Soroush Nasiriany, Chen Wang, Rohun Kulkarni, Li Fei-Fei, Silvio Savarese, Yuke Zhu, and Roberto Martin-Martin.
\newblock What matters in learning from offline human demonstrations for robot manipulation.
\newblock In \emph{Proceedings of the 5th Conference on Robot Learning}, PMLR 164:1678--1690, 2022.

\bibitem{hoque2021thrifty}
Ryan Hoque, Ashwin Balakrishna, Ellen Novoseller, Albert Wilcox, Daniel S. Brown, and Ken Goldberg.
\newblock ThriftyDAgger: Budget-aware novelty and risk gating for interactive imitation learning.
\newblock In \emph{Proceedings of the 5th Conference on Robot Learning}, PMLR 164:598--608, 2022.

\bibitem{cai2025aim}
Haoyuan Cai, Zhenghao Peng, and Bolei Zhou.
\newblock Robot-gated interactive imitation learning with adaptive intervention mechanism.
\newblock \emph{arXiv preprint arXiv:2506.09176}, 2025.

\bibitem{chua2018pets}
Kurtland Chua, Roberto Calandra, Rowan McAllister, and Sergey Levine.
\newblock Deep reinforcement learning in a handful of trials using probabilistic dynamics models.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2018.

\bibitem{janner2019mbpo}
Michael Janner, Justin Fu, Marvin Zhang, and Sergey Levine.
\newblock When to trust your model: Model-based policy optimization.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2019.

\bibitem{guo2017calibration}
Chuan Guo, Geoff Pleiss, Yu Sun, and Kilian Q. Weinberger.
\newblock On calibration of modern neural networks.
\newblock In \emph{Proceedings of the 34th International Conference on Machine Learning}, PMLR 70:1321--1330, 2017.

\bibitem{henderson2018deeprlmatters}
Peter Henderson, Riashat Islam, Philip Bachman, Joelle Pineau, Doina Precup, and David Meger.
\newblock Deep reinforcement learning that matters.
\newblock \emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 32(1), 2018.

\bibitem{agarwal2021statisticalprecipice}
Rishabh Agarwal, Max Schwarzer, Pablo Samuel Castro, Aaron Courville, and Marc G. Bellemare.
\newblock Deep reinforcement learning at the edge of the statistical precipice.
\newblock \emph{arXiv preprint arXiv:2108.13264}, 2021.

\bibitem{wilson1927score}
Edwin B. Wilson.
\newblock Probable inference, the law of succession, and statistical inference.
\newblock \emph{Journal of the American Statistical Association}, 22(158):209--212, 1927.

\end{thebibliography}
