\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{url}

\graphicspath{{figures/}}

\title{Cost-Matched Diagnostics for Human-Attention Allocation in Human-in-the-Loop Robot Learning}
\author{FORESIGHT-HIL Manuscript Draft}
\date{July 2, 2026}

\begin{document}

\maketitle

\begin{abstract}
Human-in-the-loop reinforcement learning can improve robot learning by injecting corrective actions when autonomous exploration is unsafe, slow, or unproductive. In robot-learning systems, however, an intervention trigger is not merely a control heuristic; it is a policy for allocating scarce human attention. Claims about trigger quality therefore depend on whether human cost, checkpoint variance, and budget timing are measured with enough discipline to support an allocation claim. This paper frames FORESIGHT-HIL as a diagnostic evaluation protocol for human-attention allocation rather than as a current trigger-superiority claim. In a robosuite manipulation case study, an initially plausible learning-value trigger is overturned by cost matching: a lower-budget random baseline reaches higher repeated success at lower realized human-step cost than LV-VoI scale3. Two lightweight trigger repairs remain dominated, and intervention traces show that the failure is not simply a far-from-object querying problem. The contribution is a reproducible automation-science protocol for stress-testing HIL-RL trigger claims with cost-matched random families, repeated checkpoint evaluation, and trace-level budget diagnostics before expanding new trigger designs.
\end{abstract}

\section*{Note to Practitioners}
This paper is motivated by robot-learning workflows in which human corrections are useful but expensive. The practical lesson is that a learned intervention trigger should be treated as an attention-allocation policy, not accepted because it beats one arbitrary random budget or one favorable checkpoint. Before such a trigger is deployed, scaled to more tasks, or used to justify human-efficiency claims, practitioners should sweep random intervention budgets around the trigger's realized human-step cost, evaluate selected checkpoints repeatedly, inspect when interventions start, and stop a trigger variant when same-seed random baselines dominate it in both success and cost. The present experiments use a scripted privileged-state oracle in simulation rather than real teleoperators, so the numerical results should be read as a reproducible evaluation gate, not as a direct measurement of human workload. The accompanying artifact structure exposes the evidence registry, command templates, registry-generated tables, and trace fields needed to reproduce the diagnostic before adapting it to real users or hardware.

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_protocol_setup}
\input{sections/04_results}
\input{sections/05_discussion}
\input{sections/06_conclusion}
\appendix
\input{sections/07_reproducibility_inventory}
\clearpage
\input{sections/99_references}

\end{document}
